---
title: "Statistical tests of moss removal experiment"

author: "Andrew Kleinhesselink"
date: "2019-05-02"
output:
  pdf_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(tidyverse)
library(lme4)
library(stringr)
library(pander)
library(emmeans)

panderOptions('round',c(2,2,2,2,2, 1, 3))
panderOptions('digits',10)
panderOptions('keep.trailing.zeros',TRUE)
panderOptions('table.split.table', 85)

load(file = '~/Dropbox/projects/moss_analysis/output/experiment_models.rda')

make_lrt_table <- function(m1) { 
  m2 <- update(m1, . ~ . - position:treatment)
  m3 <- update(m2, . ~ . - treatment)
  m4 <- update(m3, . ~ . - position)
  
  LRT_table <- broom::tidy( anova(m4, m3, m2, m1))
  
  LRT_table <- 
    LRT_table %>% 
    dplyr::select(-BIC, -df ) %>% 
    rename( '$\\chi^2$' = statistic ) %>% 
    rename( 'Df' = Chi.Df) %>%
    rename( 'P(>$\\chi^2$)' = p.value ) %>% 
    mutate( term = factor(term, labels = c('position:treatment', 'treatment', 'position', 'NULL' )))
  
  return(LRT_table)
}


make_infls_table <- function(m_infls){ 
  
  temp_table <- broom::tidy( anova( m_infls, test = 'F') )

  temp_table %>% 
    rename( 'Df~denom~' = Resid..Df, 
          'Res. Dev.' = Resid..Dev, 
          'F-val' = statistic, 
          'P(>F)' = p.value) %>% 
    pander
}

make_mct_table <- function( emtab ) { 
  
  
  mctab <- broom::tidy ( emtab$contrasts ) 
  
  if( 'position' %in% names(mctab) ) { 
    
    mctab <- 
      mctab %>% 
      mutate( position = str_extract(position, pattern = '^[A-Za-z]+')) 
  }
  
  
  if( "z.ratio" %in% names(mctab) ){ 
    
    mctab <- 
      mctab %>% 
      rename('z-val' = z.ratio, 
             'p-val' = p.value)
  
  }else if( "statistic" %in% names(mctab)){ 
    
    mctab <- 
      mctab %>% 
      rename('t-val' = statistic, 
             'p-val' = p.value)
  }
  
  mctab <- 
    mctab %>% 
    mutate( level1 = str_trim(str_remove_all(level1, 'patch'))) %>% 
    unite("Contrast", c('level1', 'level2'), sep = ' - ' )
  
  return(mctab)
}

```

These tables here give the statistics reported in the results section of "Effects of native bryophytes on exotic grass invasion across an environmental gradient". 


### Table 1. Fixed effects on Bromus survival
```{r echo=FALSE, warning=FALSE}

B_surv_table <- make_lrt_table(bm1)
pander(B_surv_table)

```

-----------------------------------

### Table 2. Multiple comparison test Bromus survival. Results are given on the log odds ratio (not the response) scale. P-values are adjusted by Sidak method for 15 tests. 
```{r echo=FALSE, warning=FALSE, message = FALSE}

bm_emeans <- emmeans(bm1, pairwise ~ treatment * position, adj = 'sidak' )

panderOptions('round',2)

CLD(bm_emeans, adjust = 'sidak', Letters = letters) %>% 
  arrange( position) %>%  
  pander()

panderOptions('round',c(2,2,2,2,2,3))

```

-----------------------------------

### Table 3. Fixed effects on Bromus aboveground biomass
```{r echo=FALSE, warning=FALSE}

B_mass_table <- make_lrt_table(bb1)
pander(B_mass_table)


```

-----------------------------------


### Table 4. Multiple comparison test Bromus biomass.  P-values are adjusted by Sidak method for three tests. 
```{r echo=FALSE, warning=FALSE}

bb2 <- update(bb1, . ~ . - treatment:position)
bb_emeans_no_interaction <- emmeans(bb2, pairwise ~ treatment, adj = 'sidak')  # no treatment*position effect so use only treatment 

panderOptions('round',2)

CLD(bb_emeans_no_interaction, adjust = 'sidak', Letters = letters) %>% 
  arrange(treatment) %>% 
  pander()

panderOptions('round',c(2,2,2,2,2, 1, 3))

```

-----------------------------------


### Table 5. Fixed effects on Bromus inflorescence production
```{r echo=FALSE, warning=FALSE}


make_infls_table(bf1_glm_qpois)

```
-----------------------------------

### Table 6. Multiple comparison Bromus inflorescence numbers. Results are given on the log (not the response) scale. P-values are adjusted by Sidak method for three tests. 
```{r echo=FALSE, warning=FALSE}

bf_emeans <- emmeans(bf1_glm_qpois, pairwise ~ treatment * position , adj = 'sidak')

panderOptions('round',2)

CLD(bf_emeans, adjust = 'sidak', Letters = letters) %>% 
  arrange( position) %>% 
  pander()

panderOptions('round',c(2,2,2,2,2, 1, 3))


```

-----------------------------------


### Table 7. Fixed effects on Vulpia survival
```{r echo=FALSE, warning=FALSE}


V_surv_table <- make_lrt_table(vm1)
pander(V_surv_table)

```
-----------------------------------

### Table 8. Multiple comparison for Vulpia survival. Results are given on the log odds ratio (not the response) scale. P-values are adjusted by Sidak method for three tests. 
```{r echo=FALSE, warning=FALSE, message = FALSE}

vm2 <- update(vm1, . ~ . - treatment:position)  # no signifcant interaction effect 
vm_emeans_no_interaction <- emmeans(vm2, pairwise ~ treatment, adj = 'sidak') # no position x treatment effect or position effect 

panderOptions('round',2)

CLD(vm_emeans_no_interaction, adjust = 'sidak', Letters = letters) %>% 
  arrange( treatment ) %>% 
  pander()

panderOptions('round',c(2,2,2,2,2, 1, 3))
```

-----------------------------------


### Table 9. Fixed effects on Vulpia aboveground biomass
```{r echo=FALSE, warning=FALSE}


V_mass_table <- make_lrt_table(vb1)
pander(V_mass_table)



```
-----------------------------------


### Table 10. Fixed effects on Vulpia inflorescence production
```{r echo=FALSE, warning=FALSE}


make_infls_table(vf1_glm_qpois)

```

-----------------------------------


### Table 11. Model summary for Bromus survival
```{r echo = F}

summary(bm1)

```
----------------------------------- 


### Table 12. Model summary for Bromus biomass 
```{r echo = F}

summary(bb1)

```
----------------------------------- 

### Table 13. Model summary for Bromus inflorescence production 
```{r echo = F}

summary(bf1_glm_qpois)

```
----------------------------------- 

### Table 14. Model summary for Vulpia survival
```{r echo = F}

summary(vm1)

```
----------------------------------- 

### Table 15. Model summary for Vulpia biomass 
```{r echo = F}

summary(vb1)

```
----------------------------------- 


### Table 16. Model summary for Vulpia inflorescence production 
```{r echo = F}

summary(vf1_glm_qpois)

```
----------------------------------- 

