---
title: "Statistical Tables for Vascular Plant Association with Moss"
author: "Andrew Kleinhesselink"
date: "12/18/2018"
output: 
  word_document:
    reference_docx: 
      word-style-template.docx
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
library(tidyverse)

load(file = '~/Dropbox/projects/moss_manuscript/output/point_intercept_models.rda')

```


### Table 1. Summary of linear model for moss cover across the gradient 
```{r echo = F}

summary(moss_cover_lm)

```

----------------------------------- 

### Table 2. Model summary for all vascular plant species association with moss across the gradient 
```{r echo = F}

summary(all_hits_glm)

```

--------------- 

### Table 3. F-tests all vascular plant species association with moss
```{r echo = F}

anova(all_hits_glm, test = 'F')

```

---------------------- 

### Table 4. Model summary for exotic species association with moss across the gradient
```{r echo = F}

summary(em1)

```

--------------------- 

### Table 5. F-tests for fixed effects of exotic species association with moss 
```{r echo = F}

anova(em1, test = 'F')

```

-------------------- 

### Table 6. Model summary for native species association with moss across the gradient
```{r echo = F}

summary(nm1)

```

-------------------- 

### Table 7. F-tests for fixed effects of native species association with moss 
```{r echo = F}

anova(nm1, test = 'F')

```

-------------------- 

### Table 8. Model summary for annual exotic grass association with moss across the gradient
```{r echo = F}

summary(agm1)

```

### Table 9. F-tests for fixed effects of annual exotic grass association with moss 
```{r echo = F}

anova(agm1, test = 'F')

```

-------------------- 


### Table 10. Model summary for Vulpia association with moss across the gradient
```{r echo = F}

summary(vm1)

```

-------------------- 

### Table 11. F-tests for fixed effects of Vulpia association with moss 
```{r echo = F}

anova(vm1, test = 'F')

```

-------------------- 

### Table 12. Model summary for Bromus association with moss across the gradient
```{r echo = F}

summary(bm1)

```

-------------------- 

### Table 13. F-tests for fixed effects of Bromus association with moss 
```{r echo = F}

anova(bm1, test = 'F')

```
